---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Out-of-treatment testing (oottest)

<!-- badges: start -->
<!-- badges: end -->

oottest implements the out-of-treatment testing from Kuelpmann and Kuzmics (2020). Out-of treatment testing allows for a direct, pairwise likelihood comparison of theories, calibrated with pre-existing data.

## Installation

You can install the development version of oottest from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("PhilippKuelpmann/oottest")
```

## Example

This is a basic example on how you can use the package:

(Simple test for 2 theories)

```{r example_vuong_score, eval=F, echo=T}
library(oottest)
data_experiment <- c(1,2,3)
prediction_theory_1 <- c(1/3,1/3,1/3)
prediction_theory_2 <- c(1/4,1/4,1/2)
vuong_statistic(data_experiment, pred_I = prediction_theory_1, pred_J = prediction_theory_2)
```

This is a basic example how to compare three theories:

```{r example_vuong_matrix, eval=F, echo=T}
library(oottest)
treatment_1 <- c(1,2,3)
treatment_2 <- c(3,2,1)
data_experiment <- data.frame(treatment_1, treatment_2)
theory_1 <- matrix(c(1/3,1/3,1/3, 1/3, 1/3, 1/3), nrow = 3, ncol=2)
theory_2 <- matrix(c(1/4,1/4,1/2,1/2,1/4,1/4), nrow = 3, ncol=2)
theory_3 <- matrix(c(1/3,1/3,1/3, 1/4,1/4,1/2), nrow = 3, ncol=2)
theories <- array(c(theory_1,theory_2,theory_3), dim=c(3,2,3))
vuong_matrix(data_experiment, theories)
```





