---
title: "Reproduce Külpmann, Kuzmics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{reproduce_paper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


devtools::build_vignettes()

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("oottest")
library("xtable")
```


## Loading data and predictions

The data as well as the predictions from Külpmann Kuzmics (2020) are part of this package.

Access them as:
data_two_action_games (TODO: link to man page)
data_three_action_games (TODO: link to man page)
predictions_two_action_games (TODO: link to man page)
predictions_three_action_games (TODO: link to man page)


## Recreating tables from the paper
### Calculating likelihoods

TODO: 
- create class for vuong table/matrix
- methods to add:
  - colored
  - get LHs
  - individual tests (not corrected for multiple testing)

```{r}
llh_table_2 <- create_likelihood_table(data_two_action_games, predictions_two_action_games)
llh_table_2 <- create_likelihood_table(data_two_action_games, predictions_two_action_games)
llh_table_3 <- create_likelihood_table(data_three_action_games, predictions_three_action_games)
llh_table_all <- cbind(llh_table_2,llh_table_3)
```


### Comparison of log-likelihood differences
Table 1

Graph is created in latex, using the here created files as input
theories used are:
NA-RA,CH-RA (normalized to 1), QLK-RA, QCH-RA

TODO: Set filepath

```{r}
theories <- c("NE-RA", "CH-RA", "QLK-RA", "QCH-RA")
baseline <- llh_table_all["CH-RA", ]
output <- c()
for (theory in theories) {
  lh_diff <- round(llh_table_all[theory,] - baseline, 12)
  treatment <- 1:40
  output <- cbind(treatment, lh_diff)
  write.csv(output, file= paste0(theory, ".csv"), row.names = FALSE, quote = FALSE)
}
```


### Vuong tables

```{r, results='hide'}
vuong_table_hdg <- vuong_matrix(data_two_action_games[,1:10], predictions_two_action_games[,1:10,])
vuong_table_mp1 <- vuong_matrix(data_two_action_games[,11:15], predictions_two_action_games[,11:15,])
vuong_table_mp2 <- vuong_matrix(data_two_action_games[,16:20], predictions_two_action_games[,16:20,])
vuong_table_ac <- vuong_matrix(data_three_action_games[,1:10], predictions_three_action_games[,1:10,])
vuong_table_rsp1 <- vuong_matrix(data_three_action_games[,11:15], predictions_three_action_games[,11:15,])
vuong_table_rsp2 <- vuong_matrix(data_three_action_games[,16:20], predictions_three_action_games[,16:20,])
color_vuong_table(vuong_table_hdg)
color_vuong_table(vuong_table_mp1)
color_vuong_table(vuong_table_mp2)
color_vuong_table(vuong_table_ac)
color_vuong_table(vuong_table_rsp1)
color_vuong_table(vuong_table_rsp2)
```

## Recreating tables from the Online Appendix

### Log-likelihoods
requires the creation of llh from above

```{r, results='hide'}
xtable(llh_table_2, type = "latex")
xtable(llh_table_3, type = "latex")
```

### Vuong Scores

TODO: add function for vuong table with different number of actions

```{r, results='hide'}
vuong_table_2 <- vuong_matrix(data_two_action_games, predictions_two_action_games)
vuong_table_3 <- vuong_matrix(data_three_action_games, predictions_three_action_games)
```

```{r}
# (llr_2 + llr_3)/((variance_2 + variance_3))^(.5)
num_theories <- dim(predictions_two_action_games)[3]
result <- matrix(, nrow = num_theories, ncol = num_theories)
for (i in 1:num_theories) {
  for (j in 1:num_theories) {
    llr_2 <- oottest:::get_llr(data_two_action_games, predictions_two_action_games[,,i], predictions_two_action_games[,,j])
    llr_3 <- oottest:::get_llr(data_three_action_games, predictions_three_action_games[,,i], predictions_three_action_games[,,j])
    variance_2 <- oottest:::get_variance_of_llr(data_two_action_games, predictions_two_action_games[,,i], predictions_two_action_games[,,j])
    variance_3 <- oottest:::get_variance_of_llr(data_three_action_games, predictions_three_action_games[,,i], predictions_three_action_games[,,j])
    result[i, j] <- (llr_2 + llr_3) / (variance_2 + variance_3)^(.5)
  }
}
colnames(result) <- colnames(predictions_two_action_games[1,,])
rownames(result) <- colnames(predictions_two_action_games[1,,])
vuong_table_all <- result
```

```{r, results='hide'}
  color_vuong_table(vuong_table_2)
  color_vuong_table(vuong_table_3)
  color_vuong_table(vuong_table_all)
```

### Testing theories individually
TODO: make method of vuong matrix
TODO: Surpress calculation of chi-sq p-value on treatment level (generates warnings)

```{r, results='hide', warning=FALSE}
chi_sq_hdg <- get_all_chi_sq(data_two_action_games[,1:10], predictions_two_action_games[,1:10,])
chi_sq_mp1 <- get_all_chi_sq(data_two_action_games[,11:15], predictions_two_action_games[,11:15,])
chi_sq_mp2 <- get_all_chi_sq(data_two_action_games[,16:20], predictions_two_action_games[,16:20,])
chi_sq_2 <- get_all_chi_sq(data_two_action_games, predictions_two_action_games)
chi_sq_ac <- get_all_chi_sq(data_three_action_games[,1:10], predictions_three_action_games[,1:10,])
chi_sq_rsp1 <- get_all_chi_sq(data_three_action_games[,11:15], predictions_three_action_games[,11:15,])
chi_sq_rsp2 <- get_all_chi_sq(data_three_action_games[,16:20], predictions_three_action_games[,16:20,])
chi_sq_3 <- get_all_chi_sq(data_three_action_games, predictions_three_action_games)

table_2 <- cbind(chi_sq_hdg, chi_sq_mp1, chi_sq_mp2, chi_sq_2)
table_3 <- cbind(chi_sq_ac, chi_sq_rsp1, chi_sq_rsp2, chi_sq_3)
xtable(table_2, type = "latex", digits=c(0,2,8,2,8,2,8,2,8))
xtable(table_3, type = "latex", digits=c(0,2,8,2,8,2,8,2,8))
```


### Predictions
```{r, results='hide'}
pred_2 <- round(predictions_two_action_games, 3)
th_names <- names(predictions_two_action_games[1,1,])
output <- c()
for (theory in th_names) {
  output <- rbind(output, paste0("(", pred_2[1,,theory], ", ", pred_2[2,,theory], ")"))
}
colnames(output) <- names(predictions_two_action_games[1,,1])
rownames(output) <- th_names
xtable(output, type = "latex")

pred_3 <- round(predictions_three_action_games, 3)
output <- c()
for (theory in th_names) {
  output <- rbind(output, paste0("(", pred_3[1,,theory], ", ", pred_3[2,,theory], ", ", pred_3[3,,theory],  ")"))
}
colnames(output) <- names(predictions_two_action_games[1,,1])
rownames(output) <- th_names
xtable(output, type = "latex")
```

### Data
```{r, results='hide'}
xtable(data_two_action_games, type = "latex", digits=0)
xtable(data_three_action_games, type = "latex", digits=0)
```

